Social Computing Article\thanks{This title is temporary}

### 2013-01-07 Article.tex
Corrigi algumas coisas no meu texto e consegui adicionar um pouco da notação que tava faltando

We developed a system in which the environment of the sudoku problem-solving social network presented in~\cite{farenzena:collabem} could be modelled through autonomous agent networks and analysed through a series of experiments. The optimization technique of {\em Memetic Networks}~\cite{lamb:memenet} was employed on the modelling, providing a basis for the dynamics of the agent network.

@@

Our solution adapts the {\em Memetic Newtork} technique - originally intended for use in optimization problems - to the context of constraint satisfaction problems. In this specific case (sudoku solving), we treat problems with one unique solution. To deal with this scenario, we propose a {\em Memetic Network} variation in which each agent encodes not a complete, but a partial solution to the problem.

Our solution employs a fixed topology for the agent network and models cooperation through a set of {\em aggregation rules} and reasoning through a set of {\em appropriation rules}. Our aggregation rules specify how sudoku partial solutions are copied from agent to agent, while our appropriation rules specify how agents increment these solutions with sudoku solving techniques such as naked singles, swordfish, etc.

@@

This rule employs the intuitive strategy of copying from the neighbour with the most filled sudoku, namely the most complete solution.

@@

We know that users tend to copy the first (from left to right) solutions on the graphic interface~\cite{farenzena:collabem}. The authors have provided us with a mathematical model of this behaviour, stated as $X(k) = (1-p)^{k-1}p$, where the parameter $p$ is fixed as $p = 0.5479$ and $X(k)$ denotes the probability of an agent copying the $k_{th}$ neighbour solution.

@@

In sudoku strategy literature, as in chess, we find multiple techniques with iconic names~\cite{davis:mathsudoku}. Some popular examples are {\em naked singles}, {\em naked twins}, {\em swordfish}. These strategies intend to, given a sudoku puzzle in a partial state of completion, generate movements to mark blank cells of the puzzle, as "{\em mark cell 1 of column 3 with value 5}". We reproduced a variety of these strategies, modelling each one of them as a function that maps a sudoku partial solution to a set of movements.

@@

This technique marks a sudoku cell with a value only if this cell is the last blank cell on its row, column or $3 \times 3$ block.

@@

This rule marks a sudoku cell with value $v$ only if $v$ is the single possible value to mark that cell. The other values must have been eliminated through a process of verifying that they are all present in the span encompassing the cell's row, column and $3 \times 3$ block.

>>>>

We developed a system in which the environment of the {\em Sudoku} problem-solving social network presented in~\cite{farenzena:collabem} could be modelled through autonomous agent networks and analysed through a series of experiments. The optimization technique of {\em Memetic Networks}~\cite{lamb:memenet} was employed on the modelling, providing a basis for the dynamics of the agent network.

@@

Our solution adapts the {\em Memetic Newtork} technique - originally intended for use in optimization problems - to the context of constraint satisfaction problems. In this specific case ({\em Sudoku} solving), we treat problems with one unique solution. To deal with this scenario, we propose a {\em Memetic Network} variation in which each agent encodes not a complete, but a partial solution to the problem.

Our solution employs a fixed topology for the agent network and models cooperation through a set of {\em aggregation rules} and reasoning through a set of {\em appropriation rules}. Our aggregation rules specify how {\em Sudoku} partial solutions are copied from agent to agent, while our appropriation rules specify how agents increment these solutions with {\em Sudoku} solving techniques such as naked singles, swordfish, etc.

@@

This rule employs the intuitive strategy of copying from the neighbour with the most filled {\em Sudoku} board, namely the most complete solution.

@@

We know that users tend to copy the first (from left to right) solutions on the graphic interface~\cite{farenzena:collabem}. The authors have provided us with a mathematical model of this behaviour, stated as $\langle X(k)\rangle = (1-p)^{k-1}p$, where the parameter $p$ is fixed as $p = 0.5479$ and $\langle X(k)\rangle$ denotes the probability of an agent copying the $k_{th}$ neighbour solution.

@@

In {\em Sudoku} strategy literature, as in chess, we find multiple techniques with iconic names. Some popular examples are the {\em naked singles} rule, the {\em naked twins} rule and the {\em swordfish} rule, studied in ~\cite{davis:mathsudoku}. These strategies intend to, given a {\em Sudoku} puzzle in a partial state of completion, generate movements to mark blank cells of the puzzle, as "{\em mark cell 1 of column 3 with value 5}". We reproduced a variety of these strategies, modelling each one of them as a function that maps a {\em Sudoku} partial solution to a set of movements.

@@

This technique marks a {\em Sudoku} cell with a value only if this cell is the last blank cell on its row, column or $3 \times 3$ block.

@@

This rule marks a {\em Sudoku} cell with value $v$ only if $v$ is the single possible value to mark that cell. The other values must have been eliminated through a process of verifying that they are all present in the span encompassing the cell's row, column and $3 \times 3$ block.
